---
title: "README"
author: "Binu Mathew"
date: "March 27, 2018"
output: html_document
---
# david2014 data package

This package contains one phyloseq object of data from David et al.(2014). It contains data from following samples:

   1. Saliva microbiota samples collected from Subject_A between days 26 and 364 of study
   2. Gut microbiota samples from Subject_A collected between days 0 and 364 of study
   3. Only gut microbiota samples was collected from Subject_B between study days 0 and 252.
Data processing code is available in inst/exdata 
Further information regarding the study can be obtained from https://genomebiology.biomedcentral.com/articles/10.1186/gb-2014-15-7-r89.

This phyloseq object contains:

   1. otu_table: which contains OTU counts processed from DNA reads using QIIME analysis pipeline (v1.3).
   2. tax_table: created by using Greengenes database as reference http://aem.asm.org/content/72/7/5069.long
   3. sam_data: it contains metadata



# Installing package 


```{r}
install_github("binmat/david2014")
```


# Using the package 


```{r}
library(david2014)
data(david2014)
david2014
```

